\papertitle

### 2020-01-26 paper/paper.tex
Lucy + me

>>>>

Now:
\begin{enumerate}
  \item User runs Cylc to start a suite
  \item Cylc parses the suite file, generate dependencies and generate a schedule for the execution
  \item Once a task can be executed because dependencies are ready: Cylc generates on the fly a Slurm script with the required metadata for SLURM and invoking the user-defined script for that task and then runs Slurm to queue the script
  \item Slurm queues the task and once the task is ready to be dispatched it is started on the supercomputer
  \item The shell-script executes the users-provided instructions, some of those are to generate file names using Cylc and the variables that are generated by Cylc. These filenames use templates provide by the user that define the storage location to be used.
  \item User-specified applications run taking the filenames as instructed.
  The application may use NetCDF or XIOS to perform the IO.

Our Plan:

\begin{enumerate}
  \item User runs Cylc to start a suite.
  \item Cylc parses the suite file, generate dependencies and generate a schedule for the execution.

  Now, Cylc will call into EWIOScheduler to potentially reprioritize the order of execution of tasks.
  The EWIOScheduler will read the suite file and the suite-io.rc file to make suggestions but won't enforce anything.

  \item Once a task can be executed because dependencies are ready: Cylc generates on the fly a Slurm script with the required metadata for SLURM and invoking the user-defined script for that task.

  Potentially, Cylc will change the metadata of the script telling Slurm to place a job on the same nodes as a previous job to reusue local data.
  Potentially, Cylc may also add as metadata information to migrate data.

  Then runs Slurm to queue the task.

  \item Slurm queues the task and once the task is ready to be dispatched it is started on the supercomputer

  If a migration has to be performed before or after a job is run, it would do so.

  \item The shell-script executes the users-provided instructions, some of those are to generate file names using Cylc and the variables that are generated by Cylc.
  These filenames use templates provide by the user that define the storage location to be used.

  The way filenames are generated is now slightly different, using a new command that then uses ESWIOSchedule.
  The guy reads the suite file(s) and generates information for ESDM where to prioritize to place or access data. The filename hence encoded additional information.
  Potentially, we generate an esdm.conf file to reflect the specific hardware we want to use.

  \item User-specified applications run taking the filenames as instructed.
    The application may use NetCDF, XIOS

    OR ESDM

    to perform the IO.

  ESDM loads the system configuration knowing the potential targets and to schedule application-local IO.
  Application uses ESDM with the script filename, ESDM extracts the long-term schedule information and considers it during "application-local" IO scheduling.

  \item A data management service may run and purge or migrate data according to user-specifications of the information life cycle.
